A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-04-26 Cover_letter_JPM.tex
Updates from Overleaf

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

@@

The summary of holistic cancer care in this revised manuscript could be:
"
".

@@

We appreciate the reviewer for the question allowing discussing TCGA in detail.\\

@@

..
%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.

@@

\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{figure:fig_GSE2837}
\end{figure}
\clearpage
\end{MyColorPar}

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
% ???
% x
%how to apply or modify the R scripts to use on other datasets
%\begin{itemize} %summarize the elements of the workflow
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

% #####################
\subsection*{2-4}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.

@@

We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors. (please also see Figure \ref{fig:workflow}, different sources of databases)

@@

\subsection*{2-5}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

@@

@@

>>>>

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested  candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.

{ 
(ok)Result 改寫 CAMK2N1, IL19; 
Supplementary;
Discussion:
([ok] 3.2, 3.3 只留下 validated by GSE2837)
(ok)Figure_4_CAMK2N1_IL19.pdf  KM plots
(ok)table 1 (6 genes), (ok) table 2 (4 genes)

\resizebox{\linewidth}{!}{ % adjust table size to fit the page width
Table 3: CAMK2N1 (ok)
Table 4: IL19  (ok)
\label
}
six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
}
2) Since that revision, we extended holistic cancer care in the discussion section (please see Answer 1-2).

@@

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
The summary of holistic cancer care in this revised manuscript could be:
"
".

@@

We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
We modified the workflow as ...

@@

@@

@@

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
調整 workfow 更加嚴格
以增加 validation rate
The p-values are affected by the sample size, which has be described in the main text.
as following:
% ???
% x
%how to apply or modify the R scripts to use on other datasets
%\begin{itemize} %summarize the elements of the workflow
\begin{outline}
The data from TCGA database or other databases could be applied by this workflow, since modification of the R script is necessary to adapt the difference structure among datasets (e.x. data schema, table size, definition of features, number of features and their location on the table column).\\
In short, the elements of the workflow with the \{codes\} shows:\\
(please also see Figure \ref{fig:workflow})
\1 $[\# step 1 (main)]$
\{main\_marginSFP\_HNSCC.R\}
        \2 dataset retrieval from TCGA GDC data portal (in GDAC format)
%\1 $[\# step 1]$
    \2 \{TCGA\_HNSCC\_marginSFP.R\}
        \3 \underline{raw data cleaning}
        \3 \underline{data transformation and merge}
        \3 \underline{dichotomization of clinical features}
%     \item Using a serial cut from 30\% to 70\% percentile of the cohort, it could find the least P-value cutoff of the Kaplan-Meier analysis for each gene expression.
        \3 survival analysis
            \4 cut off finder by \{cutofFinder\_func\_HNSCC.R\}
%     \item The R script program could automatically scan protein-coding genes and generate the Kaplan-Meier plots and Cox's univariate/multivariate tables.
            \4 Cox modelling
\1 $[\# step 2]$
\{analysis\_export.R\}
    \2 analysis of the tables generated from \# step 1
    \2 candidate selection
%    \item Our analysis could discover the pronounced biomarkers, which impact HNSCC's survival under the stringent Bonferroni adjustment.
\1 (remark: only the \underline{underlined} portion in \{TCGA\_HNSCC\_marginSFP.R\} should be re-coded aggressively)
\end{outline}

@@

% #####################
\subsection*{2-4}
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?

@@

We appreciate the reviewer for the critical comment and modified the Introduction accordingly.
= 詳細描述 univariable and multivariable tests work
In a multivariable test, which variables were used? 
= 列出來，並且強調 surgical margin

% x
In our workflow, we utilize FirebrowseR in step 1 to receive standardized genomic and clinical data frames while avoiding data reformatting, often causing some errors. (please also see Figure \ref{fig:workflow}, different sources of databases)

@@

\subsection*{2-5}
Here is another suggestion. To maximize the use of continuous expression values, the author can build a multivariable model (e.g., logistic regression) integrating multiple genes.
=> = a gene signature with deep learning CNN
https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z

https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8

@@

\subsection*{2-6}
[Minor comments]
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
[Minor comments]
The background should be revised extensively. 
x For example, the description of the linear model should be removed. X1...Xn should be removed. 
***More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be moved to Methods.

In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 不要誇大說明 
In Figure 1, the diagram should have direction. 
加上 direction of view

The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)???

In Figure 2, unlabeled scales on the x-axis???
除去 unlabeled stick 即可立刻改進
\begin{MyColorPar}{red}

@@

%To the best of our knowledge, TCGA "HNSC"(they coded) is the only single and largest collection of whole-genome sequencing and clinical survival dataset in the field of HNSCC research so far.

\begin{figure}
\raggedleft
\includegraphics[width=14cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{figure:fig_GSE2837}
\end{figure}
\clearpage
